---
title: "paper_asso_pre"
author: "hyojunahn"
date: "2017년 10월 5일"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#association rule_assesment machine traslation data


### install.packages -> arules
install.packages("arules")



### load data



### wrangling data


```{r asds.transactions}
library(arules)
asds <- read.csv("D:/asdt_split.csv",header=FALSE)
asds.list <- split(asds$V2,asds$V1)
asds.transactions <- as(asds.list,"transactions")
asds.transactions
summary(asds.transactions)
```

##using association rule
*we follow apriori algorithm*



```{r summary rule}
rules = apriori(asds.transactions)
summary(rules)
```


Right hand side results are many things. So I need to sort.
I just want to see qa of right hand side.



```{r inspect rule}
rules_qa <- subset(rules, rhs %in% c("qa"))
inspect(rules_qa)
```


### make csv and data.frame for using another analysis

* write(rules_qa, file="D:/ruleqa.csv",sep=",",quote=TRUE,row.names=FALSE)
* rules_qa_df <- as(rules_qa,"data.frame")

* rule.list <- as.data.frame(inspect(rules))
* rule.list <- rule.list[order(rule.list$life,decreasing=TRUE),]
* rule.list
* summary(rule.list)    

where are you?



